\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}

\title{Project Progress Report}
\author{William Kingsley, Derek Jacobson, Justin McGowen}
\date{November 2019}

\begin{document}

\maketitle


So far, the work we have done for the final video has been mostly research of the algorithms we will be comparing. We have explored a bit of where each algorithm has been implemented to compare where one might be used over the other. We have also explored the time complexities of the three algorithms we are comparing. Because one of the algorithms works much faster than the other two, we are hoping to be able to show visualizations of each algorithm to demonstrate this difference.

Based off of the things we hope to show in the video, we have broken up tasks among our group members. Each of us will implement one of the algorithms we are comparing and write code in order to see the differences of each. The biggest thing we are comparing is the time complexity difference so we need to be able to sync them up so that in our visualization, similar operations happen on similar time scales.

We are still a ways away from being done with our final presentation. We need to finished with algorithm implementations and visualizations. Once this is complete, we need to start on the video. For the video, we will be talking about how each works, where they have been implemented in the past/why they were developed, and the differences, mainly in time complexity. Through the MST Inverse-Ackermann algorithm, we can explain the ackermann function and why it is so useful.

\end{document}
